---
title: "Final Project R Markdown"
author: "Annabelle Xiong"
date: "2024-02-16"
output: html_document
---
# Introduction
This report sources information from [Kaggle Medical Costs Personal  Datasets](https://www.kaggle.com/mirichoi0218/insurance) on age, sex, BMI, region, number of children, smoker status, and medical costs for a group of individuals. The analysis objectives for this project is to explore key factors that influence insurance charges.

# Dataset
```{r, Import dataset, echo=TRUE}
here::i_am("code/02_scatterplot.R")
insurance <- readRDS(
  file = here::here("output/insurance_clean.rds")
)
```

# Demographics
```{r, Create table , echo=TRUE, message=FALSE}
table1 <- readRDS(
  file = here::here("output/table1.rds")
)
table1
```

# Analysis of the data
This section produces a multiple linear regression table using mlr. It then produces a summary table using tab_model function in the gtsummary library. The intercept is statistically significant. Each one-unit in age is associated with a \$256.86 increase in insurance charges. Each one-unit increase in bmi is associated with a \$339.19	increase in insurance charges. For each additional child, the model predicts an increase in charges of \$475.50. Smokers insurance bills are \$23848.53	higher than non smokers. Being in the southeast region is associated with \$1035.02 lower insurance charges compared to the northeast. Being in the southwest region is associated with \$960.05 lower insurance charges compared to the northeast.
```{r, MLR analysis of the data}
mlr_table <- readRDS(
  file = here::here("output/Multiple_linear_regression.rds")
)
mlr_summary <- summary(mlr_table)
mlr_coefficients <- mlr_summary$coefficients

knitr::kable(as.data.frame(mlr_coefficients))
```


# Figure
This figure shows a scatter plot of The relationship between age and insurance charges. It shows that theres is a general positive correlation between age and medical bills. There seems to be three clustered spending groups.
```{r, scatterplot, echo=TRUE}
knitr::include_graphics(
  here::here("output/scatterplot.png")
)
```